---
title: "Capacity Assesment"
author: "gabriel_mutua"
date: "September 21, 2018"
output: html_document
---

## 1 Introduction
The MLIS Department undertook capacity assessment from 15th - 20th  of August 2018, in relation to Monitoring, Evaluation, Research and Learning. The purpose of the assessment was to identify the capacity gaps and develop a capacity building plan for MLIS staff.

***
### 2 Results
The analysis below was done on 43 responses from MLIS team members. 

***

```{r include=FALSE}
#load libraries
library(ggplot2)
library(dplyr)
library(reshape2)
library(plotly)

#Read data into R
cleaned_data <- read.csv("~/work/cleaned_capacity.csv", header = TRUE, strip.white=TRUE)
```


### 3 Deparments included in the survey

Analysis on the departments which took part in the survey.

```{r pressure, echo = FALSE}

by_department = group_by(cleaned_data, department)
unique_dpt = summarise(by_department, count = n())

#create a bar plot
p <- ggplot(unique_dpt, aes(department, count, fill = department)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = count), fontface = "bold") +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_text(
      colour = "#7F7F7F",
      size = 12,
      face = "bold"
    ),
    axis.title.y = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.title = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.text = element_text(
      colour = "#7F7F7F",
      size = 9,
      face = "bold"
    )
  )

ggplotly(p) %>% config(displayModeBar = T)

```
