---
title: "Capacity Assesment Survey Results"
author: "gabriel_mutua"
date: "September 21, 2018"
output: html_document
---

## **Introduction**

The MLIS Department undertook capacity assessment from 15th - 20th  of August 2018, in relation to Monitoring, Evaluation, Research and Learning. The purpose of the assessment was to identify the capacity gaps and develop a capacity building plan for MLIS staff.

***
### **1) Results**

The analysis below was done on 43 responses from MLIS team members. 

***

```{r include=FALSE}
#load libraries
library(ggplot2)
library(dplyr)
library(reshape2)
library(plotly)
library(kableExtra)

#Read data into R
cleaned_data <- read.csv("~/analysis_survey/cleaned_capacity.csv", header = TRUE, strip.white=TRUE)
```


### **1.1) MLIS Deparments** 

we asked participants which deparment they belonged, **23** participants sayed the belonged to the field monitoring departement. **Eleven (11)** participants belonged to design,data processing and analysis department and 4 belonged to data learnig department. **See the plot below**.

```{r pressure, echo = FALSE}
by_department = group_by(cleaned_data, department)
unique_dpt = summarise(by_department, count = n())

p = ggplot(unique_dpt, aes(department, count, fill = department)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = count), fontface = "bold") +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_text(
      colour = "#7F7F7F",
      size = 12,
      face = "bold"
    ),
    axis.title.y = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.title = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.text = element_text(
      colour = "#7F7F7F",
      size = 9,
      face = "bold"
    )
  )

ggplotly(p) %>% config(displayModeBar = F) %>% layout(legend = list(x = 0, y = 1))

```

***
### **1.2) MLIS Units**

MLIS has 6 units, which are:

1. Carbon and partnership **(C&P)**.
2. Data learning **(DL)**.
3. Field Monitoring Teams **(FMT)**.
4. Information systems **(IS)**.
5. Program data analysis **(DPA)**.
6. Program data management **(PDM)**.

According to the results obtained, FMT had the largest number of participants **24**, with C&P, DL and IS having **two** members each. **See the plot below**.

```{r echo = FALSE}
####
#count Unique unit
by_unit = group_by(cleaned_data, unit)
unique_unit = summarise(by_unit, count = n())

#create a bar plot
p = ggplot(unique_unit, aes(unit, count, fill = unit)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = count), fontface = "bold") +
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_text(
      colour = "#7F7F7F",
      size = 12,
      face = "bold"
    ),
    axis.title.y = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.title = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.text = element_text(
      colour = "#7F7F7F",
      size = 9,
      face = "bold"
    )
  )

ggplotly(p) %>% config(displayModeBar = F) %>% layout(legend = list(x = 1, y = 1))

```

***
### **1.3) Current Position Held**

We asked each partcipant to input his/her current position. The results are tabulated below. The table shows all unique responses from the participants of the survey. 

```{r echo = FALSE}
library(knitr)
#Analysis of unique positions reported back in the survey.
cleaned_data$position <- tolower(cleaned_data$position)

#Returns string w/o trailing whitespace
trim.trailing <- function (x)
  sub("\\s+$", "", x)
cleaned_data$position <- trim.trailing(cleaned_data$position)

#Capitilize the first word only
firstup <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}
cleaned_data$position <- firstup(cleaned_data$position)

by_position = group_by(cleaned_data, position)
unique_position = summarise(by_position, count = n())

unique_position = arrange(unique_position, desc(count))

#Display the results as a table.
kable(unique_position, caption = "All unique positions reported during the survey") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

***
### **1.4) Experience**

We asked participants experience in months both in the current possition and in the industry.  The median for expereinece in the current position was **27 months**, while the median for the experience in the industry was **49 months**.  The box plots below shows the distibutional characteristics of experience among MLIS team members.

```{r echo=FALSE}
time_current <- cleaned_data$time_current
time_industry <- cleaned_data$time_industry

bxplt_data_1 <- data.frame(group = "current", value =  time_current)
bxplt_data_2 <-
  data.frame(group = "industry", value =  time_industry)
bxplt_data <- rbind(bxplt_data_1, bxplt_data_2)

#develop a box plot for distribution of experience
p = ggplot(data = bxplt_data, aes(group, value, fill = group)) +
  geom_boxplot(
    outlier.colour = "red",
    outlier.shape = 8,
    outlier.size = 4
  ) +
  theme(
    axis.text.x = element_text(
      colour = "#7F7F7F",
      size = 12,
      face = "bold"
    ),
    axis.title.x = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    axis.text.y = element_text(
      colour = "#7F7F7F",
      size = 12,
      face = "bold"
    ),
    axis.title.y = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.title = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.text = element_text(
      colour = "#7F7F7F",
      size = 9,
      face = "bold"
    )
  )

ggplotly(p) %>% config(displayModeBar = F) %>% layout(legend = list(x = 1, y = 1))

```

***
### **1.5) Highest Level of Education Obtained**

The participants were asked to list their highest level of education obtained. The resulst are tabulated below.

```{r echo=FALSE}
cleaned_data$level_education <- tolower(cleaned_data$level_education)
cleaned_data$level_education <-
  trim.trailing(cleaned_data$level_education)
cleaned_data$level_education <- firstup(cleaned_data$level_education)
by_edlevel = group_by(cleaned_data, level_education)
unique_edlevel = summarise(by_edlevel, count = n())
unique_edlevel = arrange(unique_edlevel, desc(count))
kable(unique_edlevel , caption = "All highest level of education reported in the survey") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

***
### **1.6) Training on the Current Area of Work**

The participants were asked if they have received any training in the current area of training. Fifty eight **(58) percent** of responded said they have recived training.

```{r echo=FALSE}
training_done <- group_by(cleaned_data, training)
training_done <- summarise(training_done, count = n()) %>% mutate(Percantage = paste(round((count/sum(count)*100),0),"%", sep = ""))

training_done = arrange(training_done, desc(count))
kable(training_done, caption = "Have you received training in the current area of work?") %>% kable_styling(bootstrap_options = "striped", full_width = F)
```

Seventeen **(17)** FMT members indicated that they had received further training, while no member of C&P who indicated he/she had recieved a further training. See the plot below.

```{r echo=FALSE, message=FALSE}
training_data <- cleaned_data[, c('training', 'unit', 'department')]
grouped_training = group_by(training_data, unit)
#unit per training
unit_training <-
  summarise(grouped_training,
            Yes = sum(training == 'Yes'),
            No = sum(training == 'No'))
unit_renamed <- c("C&P", "DL", "FMT", "IS", "PDA", "PDM")
unit_training$unit <- unit_renamed

#reshaped training
shp_training <- melt(unit_training)
shp_training <- filter(shp_training, value > 0)

#plotting unit against
#create a bar plot
p = ggplot(shp_training, aes(unit, value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(
    aes(label = value),
    fontface = "bold",
    position = position_dodge(width = 1),
    vjust = 0.5
  ) +
  theme(
    axis.text.x = element_text(
      colour = "#7F7F7F",
      size = 12,
      face = "bold"
    ),
    axis.title.x = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    axis.text.y = element_text(
      colour = "#7F7F7F",
      size = 12,
      face = "bold"
    ),
    axis.title.y = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.title = element_text(
      colour = "#FE6F88",
      size = 12,
      face = "bold"
    ),
    legend.text = element_text(
      colour = "#7F7F7F",
      size = 9,
      face = "bold"
    )
  )

ggplotly(p) %>% config(displayModeBar = F) %>% layout(legend = list(x = 1, y = 1))

```

The 22 MLIS team mebers who indicated that they have received further training listed the following trainings tabulated below.

```{r echo=FALSE}
cleaned_data$training_done <- tolower(cleaned_data$training_done)
cleaned_data$training_done <- firstup(cleaned_data$training_done)
table_trainingby <- group_by(cleaned_data, training_done)
table_training <- table_trainingby %>% summarise(count = n()) %>% filter(training_done != "")

table_training = arrange(table_training, desc(count))
kable(table_training, caption = "Training done on current area of work") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

***
### **1.7) Skills in Research, Monitoring Evaluation and Learning**

MLIS members were asked to rate their skills on research, monitoring and learning in relation to their current position. The results showed that **66 percent** of MLIS members were very good at this area, while **24 percent** were avarage. See the table below.

```{r echo=FALSE} 
knowledge_by <- group_by(cleaned_data, kwld_rsch)
table_kwld <- summarise(knowledge_by, count = n()) %>% mutate(Percantage = paste(round((count/sum(count)*100),0),"%", sep = ""))

table_kwld  = arrange(table_kwld , desc(count))
kable(table_kwld , caption = "Competency in Research and M&E") %>%  kable_styling(bootstrap_options = "striped", full_width = F)

```

The survey also included a question asking if the MLIS team members required further any training in research, monitoring evaluation and learning. Ninety two **(92) percent** indicated that they are interested in  getting training.

```{r echo=FALSE}
nd_trby <- group_by(cleaned_data, need_training)
table_ndtr <- summarise(nd_trby, count = n()) %>% mutate(Percantage = paste(round((count/sum(count)*100),0),"%", sep = ""))

table_ndtr  = arrange(table_ndtr , desc(count))
kable(table_ndtr , caption = "Percentage of People in need of training") %>%  kable_styling(bootstrap_options = "striped", full_width = F)
```

***
### **1.8) Rating MLIS Team members Skills in Research.**

MLIS team members were asked to rate there understanding and ability to undertake several research tasks (Listed below) on a scale of 1 to 5, with **“1”** meaning Not knowledgeable at all, **“2”** Less knowledgeable, **“3”** A little more Knowledgeable, **“4”** “Sufficient Knowledge, and **“5”** Excellent knowledge.

The research tasks which MLIS team members were asked to rate their knowledge in are listed below. Note they are assigned code which is used in analysis in the rest of this section.

```{r echo=FALSE}
research <- read.csv("~/analysis_survey/Research_variables.csv")

kable(research, caption = "All research tasks, and their codes") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The table below shows avarage scores of each MLIS unit in reseach. The avarage score of all MLIS units was 3. Information System unit had the highest score of 4, in research. Developing Operational Research study protocols had the poor rate of all research tasks included in the survey.

```{r echo=FALSE}
by_unit = group_by(cleaned_data, unit)
avarage_research = summarise(by_unit,
                    R_var1 = round(mean(R_var1, na.rm = TRUE), 0),
                    R_var2 = round(mean(R_var2, na.rm = TRUE), 0),
                    R_var3 = round(mean(R_var3, na.rm = TRUE), 0),
                    R_var4 = round(mean(R_var4, na.rm = TRUE), 0),
                    R_var5 = round(mean(R_var5, na.rm = TRUE), 0),
                    R_var6 = round(mean(R_var6, na.rm = TRUE), 0),
                    R_var7 = round(mean(R_var7, na.rm = TRUE), 0),
                    R_var8 = round(mean(R_var8, na.rm = TRUE), 0),
                    R_var9 = round(mean(R_var9, na.rm = TRUE), 0),
                    R_var10 = round(mean(R_var10, na.rm = TRUE), 0),
                    R_var11 = round(mean(R_var11, na.rm = TRUE), 0),
                    R_var12 = round(mean(R_var12, na.rm = TRUE), 0),
                    R_var13 = round(mean(R_var13, na.rm = TRUE), 0),
                    R_var14 = round(mean(R_var14, na.rm = TRUE), 0),
                    R_var15 = round(mean(R_var15, na.rm = TRUE), 0),
                    Count = n())


avarage_research <- avarage_research %>% 
  rowwise() %>% 
  mutate(Mean=round(mean(c(R_var1,R_var2,R_var3,R_var4,R_var5,R_var6,R_var7,R_var8,R_var9,R_var10,R_var11,R_var12,R_var13,R_var14,R_var15)),0))

attach(avarage_research)
avarage_research = avarage_research %>%
  add_row(
    unit = "Mean",
    R_var1 = round(mean(R_var1), 0),
    R_var2 = round(mean(R_var2), 0),
    R_var3 = round(mean(R_var3), 0),
    R_var4 = round(mean(R_var4), 0),
    R_var5 = round(mean(R_var5), 0),
    R_var6 = round(mean(R_var6), 0),
    R_var7 = round(mean(R_var7), 0),
    R_var8 = round(mean(R_var8), 0),
    R_var9 = round(mean(R_var9), 0),
    R_var10 = round(mean(R_var10), 0),
    R_var11 = round(mean(R_var11), 0),
    R_var12 = round(mean(R_var12), 0),
    R_var13 = round(mean(R_var13), 0),
    R_var14 = round(mean(R_var14), 0),
    R_var15 = round(mean(R_var15), 0),
    Count = round(mean(Count), 0),
    Mean = round(mean(Mean), 0)
  )

kable(avarage_research, caption = "Research skills rating, per unit") %>% kable_styling(bootstrap_options = "striped", font_size = 11) 
```

***
### **1.9) Rating MLIS Team members Skills in Monitoring and Evaluation.**
MLIS team members were asked to rate there understanding and ability to undertake several monitoring and evalution tasks (Listed below) on a scale of 1 to 5, with **“1”** meaning Not knowledgeable at all, **“2”** Less knowledgeable, **“3”** A little more Knowledgeable, **“4”** “Sufficient Knowledge, and **“5”** Excellent knowledge.

The monitoring and evalution tasks which MLIS team members were asked to rate their knowledge in  are listed below. Note they are assigned code which is used in analysis in the rest of this section.

```{r echo=FALSE, message=FALSE}
mne <- read.csv("~/analysis_survey/mne_variables.csv")

kable(mne, caption = "All Monitoring and Evalution tasks, and their codes") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The table below shows that, the avarage score of MLIS under monitoring and evaluation was 2 (Less knowledgeable ). 

```{r echo=FALSE, message=FALSE}
avarage_mne = summarise(by_unit,
                        M_var1 = round(mean(M_var1, na.rm = TRUE), 0),
                        M_var2 = round(mean(M_var2, na.rm = TRUE), 0),
                        M_var3 = round(mean(M_var3, na.rm = TRUE), 0),
                        M_var4 = round(mean(M_var4, na.rm = TRUE), 0),
                        M_var5 = round(mean(M_var5, na.rm = TRUE), 0),
                        M_var6 = round(mean(M_var6, na.rm = TRUE), 0),
                        M_var7 = round(mean(M_var7, na.rm = TRUE), 0),
                        M_var8 = round(mean(M_var8, na.rm = TRUE), 0),
                        M_var9 = round(mean(M_var9, na.rm = TRUE), 0),
                        M_var10 = round(mean(M_var10, na.rm = TRUE), 0),
                        M_var11 = round(mean(M_var11, na.rm = TRUE), 0),
                        Count = n())

avarage_mne <- avarage_mne %>% 
  rowwise() %>% 
  mutate(Mean=round(mean(c(M_var1,M_var2,M_var3,M_var4,M_var5,M_var6,M_var7,M_var8,M_var9,M_var10,M_var11)),0))

attach(avarage_mne)
avarage_mne = avarage_mne %>%
  add_row(
    unit = "Mean",
    M_var1 = round(mean(M_var1), 0),
    M_var2 = round(mean(M_var2), 0),
    M_var3 = round(mean(M_var3), 0),
    M_var4 = round(mean(M_var4), 0),
    M_var5 = round(mean(M_var5), 0),
    M_var6 = round(mean(M_var6), 0),
    M_var7 = round(mean(M_var7), 0),
    M_var8 = round(mean(M_var8), 0),
    M_var9 = round(mean(M_var9), 0),
    M_var10 = round(mean(M_var10), 0),
    M_var11 = round(mean(M_var11), 0),
    Count = round(mean(Count), 0),
    Mean = round(mean(Mean), 0)
  )

kable(avarage_mne, caption = "Monitoring and Evaluation skills rating, per unit") %>% kable_styling(bootstrap_options = "striped", font_size = 11) 
```

***
### **2.0) Rating MLIS Team members Skills in Learning.**
MLIS team members were asked to rate there understanding and ability to undertake several learning tasks (Listed below) on a scale of 1 to 5, with **“1”** meaning Not knowledgeable at all, **“2”** Less knowledgeable, **“3”** A little more Knowledgeable, **“4”** “Sufficient Knowledge, and **“5”** Excellent knowledge.

The learning tasks which MLIS team members were asked to rate their knowledge in are listed below. Note they are assigned code which is used in analysis in the rest of this section.

```{r echo=FALSE}
learning <- read.csv("~/analysis_survey/learning_variables.csv")

kable(learning, caption = "All Learning tasks, and their codes") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The avarage score of MLIS in this section was 3 (A little more Knowledgeable). Data learning scored highgly in this section with a score of 4.

```{r echo=FALSE,message=FALSE}
## Analysis on learning question.
avarage_learning = summarise(by_unit,
                             L_var1 = round(mean(L_var1, na.rm = TRUE), 0),
                             L_var2 = round(mean(L_var2, na.rm = TRUE), 0),
                             L_var3 = round(mean(L_var3, na.rm = TRUE), 0),
                             L_var4 = round(mean(L_var4, na.rm = TRUE), 0),
                             L_var5 = round(mean(L_var5, na.rm = TRUE), 0),
                             L_var6 = round(mean(L_var6, na.rm = TRUE), 0),
                             L_var7 = round(mean(L_var7, na.rm = TRUE), 0),
                             L_var8 = round(mean(L_var8, na.rm = TRUE), 0),
                             L_var9 = round(mean(L_var9, na.rm = TRUE), 0),
                             L_var10 = round(mean(L_var10, na.rm = TRUE), 0),
                             L_var11 = round(mean(L_var11, na.rm = TRUE), 0),
                             L_var12 = round(mean(L_var12, na.rm = TRUE), 0),
                             L_var13 = round(mean(L_var13, na.rm = TRUE), 0),
                             L_var14 = round(mean(L_var14, na.rm = TRUE), 0),
                             Count = n())

avarage_learning <- avarage_learning %>% 
  rowwise() %>% 
  mutate(Mean=round(mean(c(L_var1,L_var2,L_var3,L_var4,L_var5,L_var6,L_var7,L_var8,L_var9,L_var10,L_var11,L_var12,L_var13,L_var14)),0))

attach(avarage_learning)
avarage_learning = avarage_learning %>%
  add_row(
    unit = "Mean",
    L_var1 = round(mean(L_var1), 0),
    L_var2 = round(mean(L_var2), 0),
    L_var3 = round(mean(L_var3), 0),
    L_var4 = round(mean(L_var4), 0),
    L_var5 = round(mean(L_var5), 0),
    L_var6 = round(mean(L_var6), 0),
    L_var7 = round(mean(L_var7), 0),
    L_var8 = round(mean(L_var8), 0),
    L_var9 = round(mean(L_var9), 0),
    L_var10 = round(mean(L_var10), 0),
    L_var11 = round(mean(L_var11), 0),
    L_var12 = round(mean(L_var12), 0),
    L_var13 = round(mean(L_var13), 0),
    L_var14 = round(mean(L_var14), 0),
    Count = round(mean(Count), 0),
    Mean = round(mean(Mean), 0)
  )
kable(avarage_learning, caption = "Learning skills rating, per unit") %>% kable_styling(bootstrap_options = "striped", font_size = 11) 
```

***
### **2.1) Rating MLIS Team members Skills in Data Collection.**
MLIS team members were asked to rate there understanding and ability to undertake several data collection tasks (Listed below) on a scale of 1 to 5, with **“1”** meaning Not knowledgeable at all, **“2”** Less knowledgeable, **“3”** A little more Knowledgeable, **“4”** “Sufficient Knowledge, and **“5”** Excellent knowledge.

The data collection tasks which MLIS team members were asked to rate their knowledge in are listed below. Note they are assigned code which is used in analysis in the rest of this section.

```{r echo=FALSE}
data_col <- read.csv("~/analysis_survey/dc_variables.csv")

kable(data_col, caption = "All Data Collection tasks, and their codes") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

The avarage score of MLIS in this section was 4 (Sufficient Knowledge). Data learning had the lowest score of 3 in this section. All other units scored 4. Planning and conducting quality assurance checks (D_Var5), had the lowest score of 3 among all other listed tasks.

```{r echo=FALSE, message=FALSE}
avarage_dcollection = summarise(by_unit,
                                D_var1 = round(mean(D_var1, na.rm = TRUE), 0),
                                D_var2 = round(mean(D_var2, na.rm = TRUE), 0),
                                D_var3 = round(mean(D_var3, na.rm = TRUE), 0),
                                D_var4 = round(mean(D_var4, na.rm = TRUE), 0),
                                D_var5 = round(mean(D_var5, na.rm = TRUE), 0),
                                D_var6 = round(mean(D_var6, na.rm = TRUE), 0),
                                D_var7 = round(mean(D_var7, na.rm = TRUE), 0),
                                D_var8 = round(mean(D_var8, na.rm = TRUE), 0),
                                D_var9 = round(mean(D_var9, na.rm = TRUE), 0),
                                D_var10 = round(mean(D_var10, na.rm = TRUE), 0),
                                Count = n())

avarage_dcollection <- avarage_dcollection %>% 
  rowwise() %>% 
  mutate(Mean=round(mean(c(D_var1,D_var2,D_var3,D_var4,D_var5,D_var6,D_var7,D_var8,D_var9,D_var10)),0))

attach(avarage_dcollection)
avarage_dcollection = avarage_dcollection %>%
  add_row(
    unit = "Mean",
    D_var1 = round(mean(D_var1), 0),
    D_var2 = round(mean(D_var2), 0),
    D_var3 = round(mean(D_var3), 0),
    D_var4 = round(mean(D_var4), 0),
    D_var5 = round(mean(D_var5), 0),
    D_var6 = round(mean(D_var6), 0),
    D_var7 = round(mean(D_var7), 0),
    D_var8 = round(mean(D_var8), 0),
    D_var9 = round(mean(D_var9), 0),
    D_var10 = round(mean(D_var10), 0),
    Count = round(mean(Count), 0),
    Mean = round(mean(Mean), 0)
  )

kable(avarage_dcollection, caption = "Data collection skills rating, per unit") %>% kable_styling(bootstrap_options = "striped", font_size = 11) 
```

***
### **2.2) Rating MLIS Team members Skills in Qualitative and Quantitative Data management, analysis, and visualization packages.**
MLIS team members were asked to rate there understanding and ability to undertake several data collection tasks (Listed below) on a scale of 1 to 5, with **“1”** meaning Not knowledgeable at all, **“2”** Less knowledgeable, **“3”** A little more Knowledgeable, **“4”** “Sufficient Knowledge, and **“5”** Excellent knowledge.

The data collection tasks which MLIS team members were asked to rate their knowledge in are listed below. Note they are assigned code which is used in analysis in the rest of this section.

```{r echo=FALSE}
Qq_analysis <- read.csv("~/analysis_survey/Qq_variables.csv")

kable(Qq_analysis, caption = "All Qualitative and Quantitative Data management, analysis, and visualization tasks, and their codes") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The avarage score of MLIS in this section was 3 (A little more Knowledgeable). Field Monitoring teams scored poorly in this section with a score of 2.

```{r echo=FALSE, message=FALSE}
avarage_qqAnalysis = summarise(by_unit,
                               Qq_var1 = round(mean(Qq_var1, na.rm = TRUE), 0),
                               Qq_var2 = round(mean(Qq_var2, na.rm = TRUE), 0),
                               Qq_var3 = round(mean(Qq_var3, na.rm = TRUE), 0),
                               Qq_var4 = round(mean(Qq_var4, na.rm = TRUE), 0),
                               Qq_var5 = round(mean(Qq_var5, na.rm = TRUE), 0),
                               Qq_var6 = round(mean(Qq_var6, na.rm = TRUE), 0),
                               Qq_var7 = round(mean(Qq_var7, na.rm = TRUE), 0),
                               Qq_var8 = round(mean(Qq_var8, na.rm = TRUE), 0),
                               Qq_var9 = round(mean(Qq_var9, na.rm = TRUE), 0),
                               Qq_var10 = round(mean(Qq_var10, na.rm = TRUE), 0),
                               Qq_var11 = round(mean(Qq_var11, na.rm = TRUE), 0),
                               Qq_var12 = round(mean(Qq_var12, na.rm = TRUE), 0),
                               Qq_var13 = round(mean(Qq_var13, na.rm = TRUE), 0),
                               Qq_var14 = round(mean(Qq_var14, na.rm = TRUE), 0),
                               Qq_var15 = round(mean(Qq_var15, na.rm = TRUE), 0),
                               Qq_var16 = round(mean(Qq_var16, na.rm = TRUE), 0),
                               Qq_var17 = round(mean(Qq_var17, na.rm = TRUE), 0),
                               Qq_var18 = round(mean(Qq_var18, na.rm = TRUE), 0),
                               Count = n())


avarage_qqAnalysis <- avarage_qqAnalysis %>% 
  rowwise() %>% 
  mutate(Mean=round(mean(c(Qq_var1,Qq_var2,Qq_var3,Qq_var4,Qq_var5,Qq_var6,Qq_var7,Qq_var8,Qq_var9,Qq_var10,Qq_var11,Qq_var12,Qq_var13,Qq_var14,Qq_var15,Qq_var16,Qq_var17,Qq_var18)),0))

attach(avarage_qqAnalysis)
avarage_qqAnalysis = avarage_qqAnalysis %>%
  add_row(
    unit = "Mean",
    Qq_var1 = round(mean(Qq_var1), 0),
    Qq_var2 = round(mean(Qq_var2), 0),
    Qq_var3 = round(mean(Qq_var3), 0),
    Qq_var4 = round(mean(Qq_var4), 0),
    Qq_var5 = round(mean(Qq_var5), 0),
    Qq_var6 = round(mean(Qq_var6), 0),
    Qq_var7 = round(mean(Qq_var7), 0),
    Qq_var8 = round(mean(Qq_var8), 0),
    Qq_var9 = round(mean(Qq_var9), 0),
    Qq_var10 = round(mean(Qq_var10), 0),
    Qq_var11 = round(mean(Qq_var11), 0),
    Qq_var12 = round(mean(Qq_var12), 0),
    Qq_var13 = round(mean(Qq_var13), 0),
    Qq_var14 = round(mean(Qq_var14), 0),
    Qq_var15 = round(mean(Qq_var15), 0),
    Qq_var16 = round(mean(Qq_var16), 0),
    Qq_var17 = round(mean(Qq_var17), 0),
    Qq_var18 = round(mean(Qq_var18), 0),
    Count = round(mean(Count), 0),
    Mean = round(mean(Mean), 0)
  )

kable(avarage_qqAnalysis, caption = "Qualitative and Quantitative Data management, analysis, and visualization packages skills rating, per unit") %>%  kable_styling(bootstrap_options = "striped", font_size = 11) 
```

***
### **2.3) Rating MLIS Team members Skills in Information Systems (IS).**

MLIS team members were asked to rate there understanding and ability to undertake several data collection tasks (Listed below) on a scale of 1 to 5, with **“1”** meaning Not knowledgeable at all, **“2”** Less knowledgeable, **“3”** A little more Knowledgeable, **“4”** “Sufficient Knowledge, and **“5”** Excellent knowledge.

The Information Systems tasks which MLIS team members were asked to rate their knowledge in are listed below. Note they are assigned code which is used in analysis in the rest of this section.

```{r echo=FALSE}
IS_analysis <- read.csv("~/analysis_survey/IF_variables.csv")

kable(IS_analysis, caption = "All Qualitative and Quantitative Data management, analysis, and visualization tasks, and their codes") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

The avarage score of MLIS in this section was 2 (Less knowledgeable). Information Systems (IS) team scored a 5 (Excellent knowledg) in this section as all other unit scored a 2. 

```{r echo=FALSE,message=FALSE}
avarage_IFSystems = summarise(by_unit,
                              IF_var1 = round(mean(IF_var1, na.rm = TRUE), 0),
                              IF_var2 = round(mean(IF_var2, na.rm = TRUE), 0),
                              IF_var3 = round(mean(IF_var3, na.rm = TRUE), 0),
                              IF_var4 = round(mean(IF_var4, na.rm = TRUE), 0),
                              IF_var5 = round(mean(IF_var5, na.rm = TRUE), 0),
                              IF_var6 = round(mean(IF_var6, na.rm = TRUE), 0),
                              IF_var7 = round(mean(IF_var7, na.rm = TRUE), 0),
                              IF_var8 = round(mean(IF_var8, na.rm = TRUE), 0),
                              IF_var9 = round(mean(IF_var9, na.rm = TRUE), 0),
                              IF_var10 = round(mean(IF_var10, na.rm = TRUE), 0),
                              IF_var11 = round(mean(IF_var11, na.rm = TRUE), 0),
                              IF_var12 = round(mean(IF_var12, na.rm = TRUE), 0),
                              IF_var13 = round(mean(IF_var13, na.rm = TRUE), 0),
                              Count = n())

avarage_IFSystems <- avarage_IFSystems %>% 
  rowwise() %>% 
  mutate(Mean=round(mean(c(IF_var1,IF_var2,IF_var3,IF_var4,IF_var5,IF_var6,IF_var7,IF_var8,IF_var9,IF_var10,IF_var11,IF_var12,IF_var13)),0))

attach(avarage_IFSystems)
avarage_IFSystems = avarage_IFSystems %>%
  add_row(
    unit = "Mean",
    IF_var1 = round(mean(IF_var1), 0),
    IF_var2 = round(mean(IF_var2), 0),
    IF_var3 = round(mean(IF_var3), 0),
    IF_var4 = round(mean(IF_var4), 0),
    IF_var5 = round(mean(IF_var5), 0),
    IF_var6 = round(mean(IF_var6), 0),
    IF_var7 = round(mean(IF_var7), 0),
    IF_var8 = round(mean(IF_var8), 0),
    IF_var9 = round(mean(IF_var9), 0),
    IF_var10 = round(mean(IF_var10), 0),
    IF_var11 = round(mean(IF_var11), 0),
    IF_var12 = round(mean(IF_var12), 0),
    IF_var13 = round(mean(IF_var13), 0),
    Count = round(mean(Count), 0),
    Mean = round(mean(Mean), 0)
  )

kable(avarage_IFSystems, caption = "Data collection skills rating, per unit") %>% kable_styling(bootstrap_options = "striped", font_size = 11) 
```


***